\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2018-01-21 document/XSGRB_sample.tex
Final notes on 2013 bursts

@@

This data formed the basis for
\#15330\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15330.gcn3}}, but is not
published elsewhere. Starting $\sim$1.5 days after the Fermi-GBM trigger, 4.5 ks
spectroscopic integration captures a modest S/N GRB afterglow continuum all the
way down to $\sim$3200 \AA. Imprinted on the continuum are absorption features,
which we identify as due to \lya, \feii,  \mgii, \mgi~at the same redshift,
which we measure to be $z = 1.874$. From the broad absorption trough due to
\lya, we infer \nh~$= 22.0 \pm 0.3$. This spectrum is taken under ESO programme
ID: 092.D-0056(A) (PI: Rau),

\subsection{GRB~131030A (z = 1.296)}

@@

@@

@@

\subsection{GRB~131231A (z =0.642)}

>>>>

\subsection{GRB~130925A (z = 0.347)}

This spectrum has already been used in GCN
\#15250\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15250.gcn3}} and is
additionally published in \citet{Schady2015} and \citet{Kruhler2015}.
Observations of this burst began with X-shooter 3.5 hours after the
\swift~trigger. 6 ks spectroscopic integration captures a heavily dust obscured
afterglow (A$_\mathrm{V} = 5.9 \pm 0.7$\citep{Greiner2014}), with the spectrum
primarily dominated by host emission lines. All the nebular lines (\oii, \hg,
\hb, \oii, \ha, \nii, \sii) are well detected at $z = 0.347$, which we as the
redshift of the GRB. This spectrum is taken under ESO programme ID:
091.A-0877(A) (PI: Schady).

@@

This data formed the basis for
\#15330\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15330.gcn3}}, but is not
published elsewhere. Starting $\sim$1.5 days after the Fermi-GBM trigger, 4.5 ks
spectroscopic integration captures a modest S/N GRB afterglow continuum all the
way down to $\sim$3200 \AA. Imprinted on the continuum are absorption features,
which we identify as due to \lya, \feii,  \mgii, \mgi~at the same redshift,
which we measure to be $z = 1.874$. From the broad absorption trough due to
\lya, we infer \nh~$= 22.0 \pm 0.3$. This spectrum is taken under ESO programme
ID: 092.D-0056(A) (PI: Rau).

\subsection{(CHECK ME - Bright un-used spectrum)GRB~131030A (z = 1.296)}

This data has not been published before. Starting 3.4 hours after the
\swift~trigger, $6\times600$ s exposure taken under good conditions, contains a
bright GRB afterglow continuum across the entire spectral coverage of X-shooter.
A myriad of absorption features are superposed on the afterglow continuum which
we identify as being caused by \SIiv, \SIii, \civ, \alii, \aliii, \znii, \crii,
\NIii, \feii, \NIii$^*$, and \feii$^*$ at $z = 1.296$. A very strong
\mgii-absorber is also detected, intervening the line-of-sight at $z = 1.164$
with lines from \SIii, \civ, \aliii, \aliii, \feii, \mnii, and many more.

@@

This spectrum has already been used to form the basis for GCN
\#15451\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15451.gcn3}} and is
additionally published in \citet{Kruhler2015}. Starting 5.8 hours after the BAT
trigger, $4\times600$ s exposure captures a modest S/N continuum across all
arms. Imprinted on the continuum are absorption features identifed as due to
\feii~and \mgii~as well as emission lines from \oii, \hd, \hg, \hb, \oiii, \ha,
and \nii. All the lines are measured at a consistent redshift of $z = 0.599$,
which we take as the redshift of the GRB.

@@

This spectrum has already been used in shaping GCN
\#15450\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15450.gcn3}} and is
additionally published in \citet{Kruhler2015}. Starting only 1.3 hours after the
\swift~trigger, a total of 4.8 ks spectroscopic integration contains a low S/N
GRB afterglow continuum across the entire spectral coverage of X-shooter. There
are deviations from the continuum at both emission and absorption. We identify
lines from \hb, \oiii, and \ha~in emission and \feii, and \mgii~in absorption.
All lines are at a consistent $z = 1.686$, which is probably the redshift of the
GRB. Absorption lines at shorter wavelengths are also detected, but at low
significance due to an apparent downturn in the continuum caused by the presence
of dust local to the burst.

@@

This spectrum has previously been used in GCN
\#15494\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15494.gcn3}}, but is not
published in a refereed paper. Starting only 68 minutes after the BAT trigger,
4.8 ks spectroscopic integration secures afterglow continuum for this bursts,
which is measured to be at $z = 4.042$. A moderate S/N GRB afterglow continuum
is detected down to $\sim$ 6100 \AA, signifying the onset of the \lya~forest,
with part of the forest also visible. Metal absorption lines from \SIii~and
\SIiv~are detected at a consistent redshift.

\subsection{GRB~131231A (z = 0.642)}

This spectrum has previously been published in \citet{Kruhler2015} and
addtionally forms the basis for GCN
\#15645\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/15645.gcn3}}. This spectrum,
observed the following year (20.2 hours after the \swift~trigger), consists of
$4\times600$ s exposures. A high S/N GRB afterglow continuum is detected all the
way though the X-shooter arms. We identify absorption features imprinted in the
continuum as caused by \feii, \mgii, and \cahk at a consistent $z = 0.642$. By
subtracting off the bright afterglow continuum, we readily detect emission lines
arising from \oii, \hg, \hb, \oiii, and \ha~in the GRB host galaxy.
